A Match Made in Landfills?

### 2023-04-25 5 Manuscript/manuscript/Manuscript.qmd
Manuscript, supplementary material, start cross-validationn

@@

Binomial generalized linear mixed models (GLMMs) were used to predict multi-drug resistance (MDR) in White Storks, with nest identification classified as a random effects parameter. Of these, the highest performing model contained the predictors landfill use index (LUI) and age (Table1). In this model, an increase in the age of the bird was associated with a higher likelihood of MDR being present (Table2), while an increase in LUI was found to be associated with a decreased likelihood of MDR presence. A second competitive model, with a 97.20% performance score, contained only age as the predictor.

@@

Linear mixed models (LMMs) were used to predict total antimicrobial gene burden in White Storks, with nest identification again classified as a random effects parameter. The global model, containing the variables landfill use index, age, sample period, and nest success, was the highest performing model (Table3). In this model, each variable was positively correlated with antimicrobial gene burden (Table4). The next highest performing model contained age as a single predictor, with a model performance score of 86.39%.

>>>>

A total of 126 fecal samples were collected from white storks from 2020 to 2021. Of note, resistance genes to tetracyclines and betalactamines were identified in 50 (39.68%) and 73 (57.94%) fecal samples, respectively. Multi-drug resistance was identified in 39 (30.95%) samples. Mean landfill use index was 0.14 across all samples from 2021, and mean nest success was 55.95% across both sampling periods.

@@

Binomial generalized linear mixed models (GLMMs) were used to predict multi-drug resistance (MDR) in white storks, with nest identification classified as a random effects parameter. Of these, the highest performing model contained the predictors landfill use index (LUI) and age (Table1). In this model, an increase in the age of the bird was associated with a higher likelihood of MDR being present (Table2), while an increase in LUI was found to be associated with a decreased likelihood of MDR presence. A second competitive model, with a 97.20% performance score, contained only age as the predictor.

@@

Linear mixed models (LMMs) were used to predict total antimicrobial gene burden in white storks, with nest identification again classified as a random effects parameter. The global model, containing the variables landfill use index, age, sample period, and nest success, was the highest performing model (Table3). In this model, each predictor variable was positively correlated with antimicrobial gene burden (Table4). The next highest performing model contained age as a single predictor, with a model performance score of 86.39%.
